gij bent 2

### 2024-12-09 paper/paper.qmd
Update introduction

To answer the two research questions stated above, we follow up on a study by Sevenants [@sevenants_zijt_2024] about *gij bent*, a linguistic innovation concerning the second person of 'to be' in Colloquial Belgian Dutch (CBD). To compute the individual variation of different language users, we will use elastic net regression, a technique suited to determining individual variation. First, we will introduce the *gij bent* CBD linguistic innovation. Then, we will describe how we modelled the linguistic profiles of the individual user with regard to this innovation using elastic net, and why we need this specific technique to answer the questions we have in this study. Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general. TODO nakijken of dit nog klopt

>>>>

To answer the two research questions stated above, we follow up on a study by Sevenants [@sevenants_zijt_2024] about *gij bent*, a linguistic innovation concerning the second person of 'to be' in Colloquial Belgian Dutch (CBD). To compute the individual variation of different language users, we will use elastic net regression, a technique suited to determining individual variation. First, we will introduce the *gij bent* CBD linguistic innovation. Then, we will introduce the dataset and describe how we modelled the linguistic profiles of the individual users with regard to this innovation using elastic net, and why we need this specific technique to answer the questions we have in this study. Next, we will show the results of our analyses, and discuss what consequences they have for usage-based alternation research in general.
